Preprocessing

### 2023-07-25 docs/presentation/preprocess.Rmd
viz: reorder factors
viz: use data folder

The file `analysis_hegs_rpr.csv` was saved from `data\derived\public\analysis_hegs_rpr.rds`.

@@

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
library(showtext)
font_add_google("Fira Sans", "Fira Sans")
```

```{r data}
analysis <- read_csv("data/analysis_hegs_rpr.csv")
source("data/constants.R")
```

@@

## Bar charts
Include animations?

```{r}
analysis %>%
  count(dat_rec)
```

@@

>>>>

The file `analysis_hegs_rpr.csv` is from `data\derived\public\analysis_hegs_rpr.rds`.

@@

# all your themes are belong to us
# library(ggthemes)
library(tidyverse)
library(magrittr)
library(showtext)
font_add_google("Fira Sans", "Fira Sans")
```

```{r data}
analysis <- readRDS("../../data/derived/public/analysis_hegs_rpr.rds")
source("data/constants.R")
```

@@

## Bar charts
Order Q5 and Q7 responses
```{r}
analysis %<>%
  mutate(across(all_of(four_level_cols), ~ factor(., levels = four_levels))) %>%
  mutate(across(all_of(five_level_cols), ~ factor(., levels = five_levels)))
```

@@

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds", compress = FALSE)
```
